Theories of deliberated choice

### 2023-11-10 simple.tex
Str unfals

\Cref{def:fals} fills the gap to obtain that $C$ holds iff it is not rejectable.
The property demands that whatever the attitude of individuals, if the attitude is not according to the claim, then it is possible to observe that it is not.
\begin{definition}
  \label{def:fals}
  A claim $C$ is \emph{falsifiable} iff
  %$\forall {\allleadstog} \in \allleadstos: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
  $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
\end{definition}
% A claim $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$,
% equivalently iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.

@@

@@

\section{Technical notes about falsification}
\begin{remark}
  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhists)^J}$.
\end{remark}

>>>>

\Cref{def:fals} fills the gap to obtain that $C$ holds iff it is not rejectable.
The property demands that whatever the attitude of individuals, if the attitude is not according to the claim, then it is possible to observe that it is not.
\begin{definition}
  \label{def:fals}
  A claim $C$ is \emph{falsifiable} iff
  $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
  %Actually we need to exclude trivial claims with an exists in supplement to forall; so that trivial claims are not falsifiable. Then the property that we seek is trivial-or-falsifiable.
\end{definition}

@@

\begin{definition}
  A claim is \emph{unfalsifiable} iff $\exists {\allleadstog} \notin C \suchthat \Theta \cap \powerset{\allleadstog} \wsub C^\wsub$.
\end{definition} 
\begin{definition}
  A non-trivial claim is \emph{strongly unfalsifiable} iff $\Theta \wsub C^\wsub$.
\end{definition}

@@

\section{Technical notes about falsification}
A claim $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$,
equivalently iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.

\begin{remark}
  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhists)^J}$.
\end{remark}
